Lemma 1

### 2021-04-18 notes/jessie-russian-lemma.tex
I think/hope this is close on that lemma

>>>>

\section{Zooming out: revisiting Rockafellar Wets}
Rockafellar and Wets define expectation of a multifunction as 
\begin{align*}
A &= \E_p \partial L(u,Y) &= cl\{\E_p V \mid V(y) \in \partial L(u,y) p-a.s. \}
\end{align*}
%written 17 April. commented out 18 April with new verison
%Let's think about the same set as before, but take the closure first.
%\begin{align*}
%Z &= cl\{\E_p V \mid V \in \V_u\}
%\end{align*}
%Let's show $Z$ yields a selection $V$ such that (a) $V \in \V_u$, (b) $\E_p V = \vec 0$.
%Applying the Aliprantis Border result, we have (a) with more info than we need, but know that $V$ is measurable.  
%If $V$ is in the boundary of $Z$, consider that there is a sequence of measurable functions in $Z$ that converges to $V$ pointwise almost everywhere, and therefore $V$ is measurable as well. \jessie{check claim??}
%
%Moreover, we can apply the DCT to show that $\E_p V = 0$, as it is the limit of a sequence of measurable functions in $Z$ s.t. $E_p V_m = \vec 0$.?
%\jessie{Need to show $\vec 0 \in \E_p \partial L(u,Y) = cl\{\E_p V \mid V(y) \in \partial L(u,y) p-a.s. \} \implies \vec 0 \in Z$}.
%If $0 \not \in Z$, then there are some sets $E_1, E_2 \subseteq \Y$ such that $V(y) \neq \partial L(u,y)$ for all $y \in E_1$ and $E_2$.
%However we claim $p(E_1) = 0$ and $p(y) = 0$ for all $y \in E_2$.
%Therefore, 
%
%
%
%We then have $V$ measurable and $q \in \ker_\P V \implies \E_q V = \vec 0 \implies \vec 0 \in \E_p \partial L(u,Y) = \partial \E_p L(u,Y) \implies u \in \Gamma(q) \implies q \in \Gamma_u$.
%Thus the proof is complete.

%new 18 Apr 21
Consider the set $Z = \{\E_p V \mid V \in \V_u\}$.
We claim that $Z = A$.
$Z \subset A$ is trivial, so it is left to show $A \subseteq Z$.

Consider $v \in A$.
There is a sequence $\{v_m\} \to v$ such that $v_m \in A$, and therefore there is a sequence $V_m$ of measurable functions in the subgradient set of $L(u,y)$ $p$-almost surely.
\jessie{Claim: $V_m \to V$, $V$ is measurable, and $\E_p V = v$.  The second is true if $V_m \to V$ pointwise almost everywhere. And third should follow as well from convergence and DCT?}

Now consider $E = \{y \in \Y \mid V(y) \in \partial L(u,y)\}$.
We have $p(E^c) = 0$ and $E \in$ the sigma algebra by definition of $p$-almost surely.
Therefore $E^c$ is in the sigma algebra.
Therefore, for all $y \in E^c$, we can set $V'(y) = 0$ and $V'(y) = V(y)$ for $y \in E$.
We have $V'$ measurable as $V'^{-1}(\{0\}) = E^c \cup \{x \mid V(x) = 0\}$, which is the union of elements of the sigma algebra, and therefore is also in the sigma algebra.  
Therefore we have
\begin{align*}
v &= \lim_{m \to \infty} v_m\\
&= \lim_{m \to \infty} \int_\Y V_m\\
&= \int_\Y V(y) dpy \jessie{DCT}\\
&= \int_{E} V(y) dpy + \int_{E^c} V(y) dpy\\
&= \int_{E} V(y) dpy\\
&= \int_{E} V'(y) dpy\\
&= \int_{E} V'(y) dpy + \int_{E^c} V'(y) dpy \\
&= \int_\Y V'(y)
\end{align*}

Therefore, $v \in Z$.
